Probabilistic Catalogs from Crowded Star Fields

### 2012-07-11 paper/ms.tex
One or two references

A fundamental problem in astronomy is the construction of {\it catalogs} from
raw image data. Essentially, the question being answered is ``given the image
we have obtained, what objects are present in the field and what are their
properties?''.

@@

@@

\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Brewer, P{\'a}rtay, 
\& Cs{\'a}nyi}{2011}]{dnest} Brewer B.~J., P{\'a}rtay L.~B.,
Cs{\'a}nyi G., 2011, Statistics and Computing, 21, 4, 649-656. arXiv:0912.2380

>>>>

A fundamental problem in astronomy is the construction of {\it catalogs} from
raw image data. Essentially, the question being answered is ``given the image
we have obtained, what objects are present in the field and what are their
properties?''. Standard tools include \texttt{SExtractor} \citep{sextractor}.

@@

\citet{2011MNRAS.415.3462F} have attempted this, by replacing the complex
$N$-component model with a single-component model, and using the
single-component
results to reconstruct what the $N$-component results would have been. However,
this will not work well in situations where there is significant confusion
(i.e. two or more sources overlap) and also does not allow for unknown $N$,
which is the general situation. What we really need is a variable dimension
sampler such as reversible jump MCMC \citep{rjmcmc}.

@@

\begin{thebibliography}{99}
\bibitem[Bertin and 
Arnouts(1996)]{sextractor} Bertin, E., Arnouts, S.\ 1996.\ SExtractor: Software for source extraction.\ Astronomy and Astrophysics Supplement Series 117, 393-404.

\bibitem[\protect\citeauthoryear{Brewer, P{\'a}rtay, 
\& Cs{\'a}nyi}{2011}]{dnest} Brewer B.~J., P{\'a}rtay L.~B.,
Cs{\'a}nyi G., 2011, Statistics and Computing, 21, 4, 649-656. arXiv:0912.2380

\bibitem[Feroz et al.(2011)]{2011MNRAS.415.3462F} Feroz, F., Balan, S.~T., 
Hobson, M.~P.\ 2011.\ Detecting extrasolar planets from stellar radial 
velocities using Bayesian evidence.\ Monthly Notices of the Royal 
Astronomical Society 415, 3462-3472.
